### 2021-08-03 paper/paper.tex
add KHI figures

>>>>

Some of the main features of \trixi are demonstrated in the following figures.
Figure~\ref{fig:kelvin_helmholtzs} demonstrates entropy-dissipative shock-capturing
methods with adaptive mesh refinement applied to a classical Kelvin-Helmholtz
flow instability problem.

\begin{figure}[htbp]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t2}
    \caption{Density at time $t = 2$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t2}
    \caption{Mesh at time $t = 2$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t3}
    \caption{Density at time $t = 3$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t3}
    \caption{Mesh at time $t = 3$.}
  \end{subfigure}%
  \caption{Numerical solutions of a Kelvin-Helmholtz instability using
           entropy-dissipative shock-capturing methods and adaptive mesh
           refinement for the compressible Euler equations.}
  \label{fig:kelvin_helmholtzs}
\end{figure}

\todo{TODO: Andrew, add gingerbread man example for acoustics} %TODO: Andrew

The detailed physical setups and numerical parameters as well as all code
necessary to reproduce these figures are available in the reproducibility
repository for this article \cite{ranocha2021adaptiveRepro}.
